A Domain Specific Language for SpectreGuard

### 2020-12-06 paper/main.tex
Lead in to analysis section

In this code, the entire contents of the secret variable \ttt{secretArray} is leaked
to the public variable \ttt{publicArray}, despite the two variables having different
sensitivity annotations and therefore type checking without error. This is the
result of information being indirectly leaked from the secret variable to the
public variable via a control flow construct: in this case, the innermost \ttt{for} loop.

\section{Information Flow Analysis}
\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...

>>>>

Even though this code type checks without error, the entire contents of the secret variable \ttt{secretArray} is leaked
to the public variable \ttt{publicArray}. The leak occurs despite the fact that the two variables have different
sensitivity annotations. This is the
result of information being indirectly leaked from the secret variable to the
public variable via a control flow construct: in this case, the innermost \ttt{for} loop.

This kind of leak directly motivates the analysis in Section \ref{sec:Analysis}. This analysis will perform
some level of checking beyond the relatively basic sensitivity type check described so far.

\section{Information Flow Analysis}
\label{sec:Analysis}
\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...
